Constraining Black Hole Growth with High-z Quasar Observations

### 2022-07-27 ms.tex
first roll fixing k comments

\title{Draft}

@@

\author[0000-0001-9840-4959]{Wenxiu Li}
\affiliation{Department of Astronomy, School of Physics, Peking University, Beijing, 100871, China}
\author[0000-0001-9840-4959]{Kohei Inayoshi}
\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
\author[0000-0001-9840-4959]{Masafusa Onoue}
\altaffiliation{Kavli Astrophysics Fellow}
\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), The University of Tokyo, Chiba 277-8583, Japan}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of black hole mass function (BHMF) and the quasar luminosity function (QLF)
plays an important role in the establishment of BH-galaxy coevolution at high redshifts ($z\gtrsim$ 6).
However, the accretion and radiation properties of growing BHs in the high-$z$ environments 
still remain a challenge to be explored.
In this work, based on a semi-analytic BH seed formation model, 
we relate the seeding time and BH masses at born with the growth tracks of their parent halos. 
We then construct the mass and luminosity evolution of the BH population with a growth model 
characterizing the episodical BH accretion and Eddington ratio distribution function (ERDF) motivated by observational constraints.
The model parameters are fitted to reproduce the observed BHMF and QLF of the quasar population down to $z\sim$ 6.
Our best-fit models suggest that BHs grow with episodical bursts and quescent phases, with time duration 
typically in units of 20 $\sim$ 30 Myr. 
In the sub-sample of massive BHs with $M\gtrsim 10^8~\Msun$, 
the duty cycle of active accretion phase is $f_{\rm duty}\sim 0.15$, 
boosted from that in the whole population by nearly a factor of two. 
We find that the intrinsic ERDF of the whole quasar population is well presented by a Schechter shape, 
indicating a large number of low Eddington ratio objects missed by the current flux-limited quasar selections.
We give prediction of the early evolution of BHMF and QLF, as well as the growth patterns of individual BHs, 
which will likely be unveied by deep and wide-field surveys with, e.g. 
the James Webb Space Telescope (JWST) and the forthcoming Roman Space Telescope (RST) and Euclid.
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S}%,1992MNRAS.259..725S}.
Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the quasar luminosity function based on multi-wavelength observations,
the cosmic BH accretion history and their radiative efficiency are nicely constrained 
\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T}.

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
% \red{KI: you could find better reference in this Decadal Survey?}.
\red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
\blue{
Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys 
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D},
with the quasar luminosity function constructed \citep[e.g.,][]{2018ApJ...869..150M}, 
and the virial BH mass investigated from the Mg II 2798 $\rm{\AA}$ line width where deep spectroscopic measurements are carried out
\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
}
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.
% \red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.

@@

\subsection{BH mass growth}
\label{sec:model}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
\blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
% The high mass BH should be strangulated by as it grows, 
\blue{
On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
we also introduce a similar functional form which defines the mass dependent function of $f(\Mbh)$ as 
%
\begin{equation}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where we adopt $M_{\bullet,c}=10^8~\Msun$.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed.
%  \blue{(references, Ueda+14?s)}.
}
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

@@

In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
converting the hard X-ray luminosity to the 1450 $\mathrm{\AA}$ magnitude with bolometric correction factors of
\begin{equation*}
  f^{\rm bol}_{\rm X} =
  a\left[1+\left(\frac{\log \left(\Lbol / L_\odot\right)}{b}\right)^{c}\right],
\end{equation*}
where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq. 2 in ][]{2020A&A...636A..73D}, 
and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
The obscuration fraction reads 
\begin{equation*}
  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ (\log \Lbol/L_\odot) -43.75] \rbrace,
\end{equation*}
following \citet{2014ApJ...786..104U}.
\blue{
An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} 
for their X-ray AGN sample with additional optical obscuration classification gives 
\begin{equation*}
  \fobsc = 0.56 + \frac{1}{\pi} \text{arctan} \frac{43.89 - (\log \Lbol/L_\odot)}{0.46}.
\end{equation*}
We also fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$ in the Appendix.
}

@@

% prior
In this analysis, we constrain those parameters to be within certain physically acceptable ranges, 
assuming a prior function for each quantity.
We use a uniform prior on $\tlife$ with a limit of $10~{\rm Myr} \leq \tlife \leq 200~{\rm Myr}$,
motivated by the constraints on the quasar lifetime based on various observations
\citep[e.g.,][]{2004cbhg.symp..169M}.
The parameter of $\delta$ that characterizes a non-exponential BH growth 
is constrained at $\log \delta$ from $-4$ to $-0.3$ 
\footnote[2]{ We first set uniform prior $0\leq \delta \leq 1$, 
and find the posterior distribution assembles to $\delta \lesssim 0.1$.
We then switch to impose the $\log \delta$ prior to improve the fitting performance at small $\delta$ values.
}, 
\red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
%slightly suppressing the growth in the high mass end. 
% After trials we find in the Markov chain, the value of $\tlife$ reduces to $\lesssim$ 100 Myr, 
% and the one for $\delta$ assembles to $\lesssim 0.1$. 
% Driven by these phenomena, we switch the uniform $\tlife$ prior to 10 to 200 Myr,
% and use $\log \delta$ instead of $\delta$ with a prior ranging from $-4$ to $-1$ in pursuit of better fitting performance. 
The prior function is uniform at $\log \delta \geq -3$ and is imposed to decay with an exponential cutoff at $\log \delta < -3$,
which is small enough for the model to be approximately mass independent.
%since toward low $\log\delta$ the model is essentially mass-independent,
%and remains uniform otherwise. 
For the characteristic Eddington ratio $\lambda_0$ in the Schechter-type ERDF, 
we impose a Gaussian prior function with a mean value of $\mu_{\lambda_0}=0.6$ and a dispersion of $\sigma_{\lambda_0}=0.4$.
% motivated by the various observations revealing a large sample of quasars with peak $\lambda\lesssim 1$,
The choice is motivated by the brightest quasar samples at $z=$ 6, whose ERDF function is peaked around $\lambda \sim 0.6$ 
% \citep[e.g.,][Onoue et al. in preparation]{2010AJ....140..546W}.
\citep[e.g.,][]{2010AJ....140..546W}.
\red{Specially a complete sample of quasars from Onoue et al. in prep peak with $\log \lambda_0 \approx -0.24 \pm 0.31$ 
before correcting the selection bias. (to be revised by MO)}.
% It is worth noting that, observationally the high-$z$ ERDF is fitted by a log-normal function. 
% \blue{
% because of detection limit, there may be a large population of low $\lambda$ BHs unrevealed,
% so our model of Schechter distribution is purely from theoretical prediction 
% and extrapolation of the statistical properties of its low-$z$ counterparts. 
% Then the slope index alpha uncertain \dots
% }
% However, lower-$z$ quasar observations reveal that ERDF is better fitted by a Schechter function \citep{2015MNRAS.447.2085S}, 
% indicating a prominent population of low $\lambda$ quasars is hidden by the flux-limited incompleteness.
For the low-$\lambda$ slope of $\alpha$ in the ERDF, we assign a Gaussian prior function with a mean value 
$\mu_{\alpha}=0$ and a dispersion of $\sigma_{\alpha}=0.3$.
Note that the value of $\alpha$ remains poorly constrained by the current high-$z$ quasar observations,
but the low-$z$ quasar samples support $-0.3 \lesssim \alpha \lesssim 0.3$ \citep[e.g., see Figure 21 in][]{2015MNRAS.447.2085S}.
% considering the more significant obscuration of lower $\lambda$ quasars 
%we assign a Gaussian prior, with the mean value $\mu_{\alpha}=0.$ and scatter $\sigma_{\alpha}=0.3$.

@@

The two parameters characterizing the ERDF are given as
$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.01$ and $0.1$, respectively.
\blue{
With those values, the number fraction of super-Eddington accreting BHs is
estimated as $P(\lambda>1)=0.064$ and 0.075, respectively. 
The small discrepancy is enlarged with the multiple cycles of assigning $\lambda$ to BH growth, 
and increase the fraction of the super-Eddington phase for smaller $\fseed$. 
Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
consistent with a general picture for the early assembly of SMBHs 
\citep[e.g.,][]{2006NewAR..50..665F,2008AJ....135.1057J,2010AJ....139..906W}.
The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
in the model would differ from those in observations.
On the other hand, the power-law index of $\alpha$ in the ERDF tends to increase as the seeding fraction decreases,
indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
Thus, with lower seeding fractions, the high-$z$ quasar assembly spends a larger fraction of time in active phases 
and reproduce the bulk properties of the BHMF and QLF.
}

@@

% where $\bar{k}_{\rm M} \equiv k_{\rm M} \ln 10 \simeq -1.84$.
% \red{KI: I'm not sure what we discuss here... One thing is the cosmic SFR density (Madau's plot).
% Is there something like Madau's plot but for DM halos?}
% The exponential dependence on redshift is reminiscent of the cosmic galaxy mass growth
% $M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio,
% and the growth rate of DM halos in the extended Press-Schechter formalism
% $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
% Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows
% an exponential evolution with redshift,
% which is statistically in agreement with the host halo and galaxy growth.
The star-to-halo mass ratio is assumed to be $f_\star =0.01$ for those quasar progenitor halos at $z>6$
% (UNIVERSEMACHINE; Behroozi et al. 2019).
\citep[fits by code {\tt UNIVERSEMACHINE} in][]{2019MNRAS.488.3143B}.
%https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.3143B/abstract
With those values, we estimate the stellar-to-BH mass ratio for high-$z$ quasars as
%
\begin{equation}
\frac{\rho_{\star}(z)}{\rho_{\bullet}(z)}
\simeq 2.5\times 10^{3} \left(\frac{f_\star}{0.01}\right)
~ 10^{(k_{\rm h}-k_{\rm M})(z-6)},
\end{equation}
% 
\red{KI: please check the value of $k_{\rm h}-k_{\rm M}$.}
\blue{
where $k_{\rm h} \approx -0.16 $ for the parent halo growth histories.
}
Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
is broadly consistent with those seen in the local universe, although SMBHs observed as high-$z$ quasars
appear to be overmassive compared to the local relation \citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P}.

>>>>

\title{Constraining Black Hole Growth with High-z Quasar Observations}

@@

\author[0000-0001-9840-4959]{Wenxiu Li}
\affiliation{Department of Astronomy, School of Physics, Peking University, Beijing, 100871, China}
\author[0000-0001-9840-4959]{Kohei Inayoshi}
\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
\author[0000-0001-9840-4959]{Masafusa Onoue}
\altaffiliation{Kavli Astrophysics Fellow}
\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), The University of Tokyo, Chiba 277-8583, Japan}
\author[0000-0003-3467-6079]{Daisuke Toyouchi}
\affiliation{Research Center for the Early Universe (RESCEU), The University of Tokyo, Hongo, 7-3-1, Bunkyo-ku Tokyo, 113-0033, Japan}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of black hole mass function (BHMF) and the quasar luminosity function (QLF)
plays an important role in the establishment of BH-galaxy coevolution at high redshifts ($z\gtrsim$ 6).
However, understanding the accretion and radiation properties of growing BHs in the high-$z$ environments 
still remains challenging.
In this work, based on a semi-analytic BH seed formation model, 
we relate BH seeds with the growth tracks of their parent halos. 
We then construct a model of BH mass and luminosity evolution 
characterizing the episodical BH accretion and Eddington ratio distribution function (ERDF).
The model parameters are fitted to reproduce the observed BHMF and QLF of the quasar population at $z\sim$ 6.
Our best-fit models suggest that BHs grow with episodical bursts and quescent phases, with time duration 
typically in units of 20 $\sim$ 30 Myr. 
The duty cycle of active accretion is $f_{\rm duty}\sim 0.15$ for massive BHs with $M\gtrsim 10^8~\Msun$, 
boosted from that in the whole population by nearly a factor of two. 
We find that the intrinsic ERDF of the whole quasar population is well presented by a Schechter shape, 
indicating a large number of low Eddington ratio objects missed by the current flux-limited quasar selections.
We give prediction of the early evolution of BHMF and QLF,
as well as the growth patterns of individual BHs, 
which will likely be unveiled by the James Webb Space Telescope (JWST) and future deep and wide-field surveys.
%  with, e.g. 
% the , Roman Space Telescope (RST), and Euclid.
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive black holes (BHs) in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S}.
%,1992MNRAS.259..725S}.
Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the quasar luminosity function based on multi-wavelength observations,
the cosmic BH accretion history and their radiative efficiency are nicely constrained 
\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T}.

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
% \red{KI: you could find better reference in this Decadal Survey?}.
Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the quasar luminosity function \citep[e.g.,][]{2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.
% \red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.

@@

\subsection{BH mass growth}
\label{sec:model}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
\blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
% The high mass BH should be strangulated by as it grows, 
On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
we introduce a similar functional form that characterizes its mass dependence 
%
\begin{equation}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where $M_{\bullet,c}=10^8~\Msun$ is adopted.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed, 
while for small BHs the growth rate is accelerated.
%  \blue{(references, Ueda+14?s)}.
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

@@

In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
converting the hard X-ray luminosity to the 1450 $\mathrm{\AA}$ magnitude with bolometric correction factors of
\begin{equation*}
  f^{\rm bol}_{\rm X} =
  a\left[1+\left(\frac{\log \left(\Lbol / L_\odot\right)}{b}\right)^{c}\right],
\end{equation*}
where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq.~2 in ][]{2020A&A...636A..73D}, 
and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
The obscuration fraction reads 
\begin{equation*}
  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ (\log \Lbol/L_\odot) -43.75] \rbrace,
\end{equation*}
following \citet{2014ApJ...786..104U}.
An alternative fitting form of $\fobsc$ based on their X-ray AGN sample with additional optical obscuration classification 
is propose by \citet{2014MNRAS.437.3550M} as
%
\begin{equation*}
  \fobsc = 0.56 + \frac{1}{\pi}~ \text{arctan} \left[ \frac{43.89 - (\log \Lbol/L_\odot)}{0.46}\right].
\end{equation*}
%
We also conduct the parameter fitting with this prescription and discuss the sensitivity of our results to 
the choice of $\fobsc$ in the Appendix.

@@

% prior
In this analysis, we constrain those parameters to be within certain physically acceptable ranges, 
assuming a prior function for each quantity.
We use a uniform prior on $\tlife$ with a limit of $10~{\rm Myr} \leq \tlife \leq 200~{\rm Myr}$,
motivated by the constraints on the quasar lifetime based on various observations
\citep[e.g.,][]{2004cbhg.symp..169M}.
The parameter of $\delta$ that characterizes a non-exponential BH growth 
is constrained at $\log \delta$ from $-4$ to $-0.3$
\footnote[2]{ We first set uniform prior $0\leq \delta \leq 1$, 
and find the posterior distribution assembles to $\delta \lesssim 0.1$.
We then switch to impose the $\log \delta$ prior to improve the fitting performance at small $\delta$ values.}.
%\red{KI: add a footnote, explaining why not $\delta$ but $\log \delta$?}.
%slightly suppressing the growth in the high mass end. 
% After trials we find in the Markov chain, the value of $\tlife$ reduces to $\lesssim$ 100 Myr, 
% and the one for $\delta$ assembles to $\lesssim 0.1$. 
% Driven by these phenomena, we switch the uniform $\tlife$ prior to 10 to 200 Myr,
% and use $\log \delta$ instead of $\delta$ with a prior ranging from $-4$ to $-1$ in pursuit of better fitting performance. 
The prior function is uniform at $\log \delta \geq -3$ and is imposed to decay with an exponential cutoff at $\log \delta < -3$,
which is small enough for the model to be approximately mass independent.
%since toward low $\log\delta$ the model is essentially mass-independent,
%and remains uniform otherwise. 
For the characteristic Eddington ratio $\lambda_0$ in the Schechter-type ERDF, 
we impose a Gaussian prior function with a mean value of $\mu_{\lambda_0}=0.6$ and a dispersion of $\sigma_{\lambda_0}=0.4$.
% motivated by the various observations revealing a large sample of quasars with peak $\lambda\lesssim 1$,
The choice is motivated by the brightest quasar samples at $z=$ 6, whose ERDF function is peaked around $\lambda \sim 0.6$ 
% \citep[e.g.,][Onoue et al. in preparation]{2010AJ....140..546W}.
\citep[e.g.,][]{2010AJ....140..546W}.
\red{Specially a complete sample of quasars from Onoue et al. in prep peak with $\log \lambda_0 \approx -0.24 \pm 0.31$ 
before correcting the selection bias. (to be revised by MO)}.
% It is worth noting that, observationally the high-$z$ ERDF is fitted by a log-normal function. 
% \blue{
% because of detection limit, there may be a large population of low $\lambda$ BHs unrevealed,
% so our model of Schechter distribution is purely from theoretical prediction 
% and extrapolation of the statistical properties of its low-$z$ counterparts. 
% Then the slope index alpha uncertain \dots
% }
% However, lower-$z$ quasar observations reveal that ERDF is better fitted by a Schechter function \citep{2015MNRAS.447.2085S}, 
% indicating a prominent population of low $\lambda$ quasars is hidden by the flux-limited incompleteness.
For the low-$\lambda$ slope of $\alpha$ in the ERDF, we assign a Gaussian prior function with a mean value 
$\mu_{\alpha}=0$ and a dispersion of $\sigma_{\alpha}=0.3$.
Note that the value of $\alpha$ remains poorly constrained by the current high-$z$ quasar observations,
but the low-$z$ quasar samples support $-0.3 \lesssim \alpha \lesssim 0.3$ \citep[e.g., see Figure 21 in][]{2015MNRAS.447.2085S}.
% considering the more significant obscuration of lower $\lambda$ quasars 
%we assign a Gaussian prior, with the mean value $\mu_{\alpha}=0.$ and scatter $\sigma_{\alpha}=0.3$.

@@

The two parameters characterizing the ERDF are given as
$(\lambda_0,\alpha) = (0.89,0.12)$ and $(0.87,0.20)$ for $\fseed=0.1$ and $0.01$, respectively.
With those values, the fraction of super-Eddington accreting BHs is estimated as $P(\lambda>1)=0.064$ and 0.075, respectively. 
While the probability of rapid accretion in each cycle is similar, multiple accretion episodes enlarge the difference.
Moreover, the best fit value of $\delta$ is $(0.001,0.055)$ for the two $\fseed$ cases,
the higher $\delta$ value encourages the growth of small BHs with $M_\bullet <10^8~\Msun$,
so that the ten-fold difference in $\fseed$ is nearly offset.
%Thus for different $\fseed$ values, a similar number density of BHs which rapidly grow to be SMBHs by $z\simeq 6$ is produced, 
%consistent with a general picture for the early assembly of SMBHs 
%\citep[e.g.,][]{2006NewAR..50..665F,2008AJ....135.1057J,2010AJ....139..906W}.
The characteristic Eddington ratio needs to be close to unity, otherwise the highest luminosity and BH mass
in the model would differ from those in observations.
On the other hand, the power-law index of $\alpha$ in the ERDF tends to increase as the seeding fraction decreases,
indicating that fraction of active BHs with $\lambda \gtrsim 1$ is elevated. 
Thus, with lower seeding fractions, the high-$z$ quasar assembly spends a larger fraction of time in active phases 
and reproduce the bulk properties of the BHMF and QLF.

@@

% where $\bar{k}_{\rm M} \equiv k_{\rm M} \ln 10 \simeq -1.84$.
% \red{KI: I'm not sure what we discuss here... One thing is the cosmic SFR density (Madau's plot).
% Is there something like Madau's plot but for DM halos?}
% The exponential dependence on redshift is reminiscent of the cosmic galaxy mass growth
% $M_{\star} \propto e^{-B z}$, as a consequnce of the assumption of fixed galaxy to DM halo mass ratio,
% and the growth rate of DM halos in the extended Press-Schechter formalism
% $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$ \citep{2008MNRAS.383..615N}.
% Our results suggest that the cumulative massive BH mass density growing in galactic nuclei also follows
% an exponential evolution with redshift,
% which is statistically in agreement with the host halo and galaxy growth.
The star-to-halo mass ratio is assumed to be $f_\star =0.01$ for those quasar progenitor halos at $z>6$
% (UNIVERSEMACHINE; Behroozi et al. 2019).
\citep[fits by code {\tt UNIVERSEMACHINE} in][]{2019MNRAS.488.3143B}.
%https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.3143B/abstract
With those values, we estimate the stellar-to-BH mass ratio for high-$z$ quasars as
%
\begin{equation}
\frac{\rho_{\star}(z)}{\rho_{\bullet}(z)}
\simeq 2.5\times 10^{3} \left(\frac{f_\star}{0.01}\right)
~ 10^{(k_{\rm h}-k_{\rm M})(z-6)},
\end{equation}
% 
where $k_{\rm h} \approx -0.16 $ for the parent halo growth histories.
Therefore, at $z\sim 6$ the bulge-to-BH mass ratio $\sim O(10^3)$ for the entire BH population (i.e., low-mass BHs and low-luminosity quasars) 
is broadly consistent with those seen in the local universe, although SMBHs observed as high-$z$ quasars
appear to be overmassive compared to the local relation \citep[e.g.,][]{2013ApJ...773...44W,2020A&A...637A..84P}.
